Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-11-20 Scripts/Initial_Analysis.Rmd
updates on figures and stock from species

plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  # scale_y_continuous("Cumulative number",expand = expand_scale(mult = c(0, .05))
  #                    ) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank()
  ) +
  guides(fill=guide_legend(title= "Level")) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 12,
  height = 7,
  units = "in"
  )

@@

Value_map_data <- Eme_value_data %>% 
  left_join(Total_value,
            by = c("fishing_entity_id","variable")) %>% 
  mutate(participation = (sum_value/tot_value)*100)

@@

Index_data <- Eez_d_hist %>% 
  left_join(Value_map_data) %>% 
  filter(
    tresh == "Tresh_one",
    metric == "mean_yr"
  ) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,variable) %>% 
  summarise(
    toe = mean(value,na.rm=T),
    # sum_value = sum(sum_value),
    mean_part = mean(participation,na.rm=T)
  ) %>% 
  filter(!is.na(variable)) %>% 
  # spread(variable,sum_value) %>% 
  spread(variable,mean_part) %>% 
  mutate(
    imp = catch+value,
    index = imp/toe
  )

@@

# Get min and maximums
min_index <- min(Index_data$index)
max_index <- max(Index_data$index)

Index_data <- Index_data %>% 
  mutate(
    index_norm =(index-min_index)/(max_index-min_index),
    index_2000 = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  )

@@

Value_map_data <- Index_data %>%
  select(sau_fishing_entity,fishing_entity_id,
         # tresh,
         # variable,
         participation = index_2000)

@@

for(i in 1:1){

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = Brazil_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = Brazil_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Vulnerabillity index",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

kruskalmc(emerging_yr~un_sub_region, data = Reg_diff_data)

@@

kruskalmc(emerging_yr~DemersPelag, data = Hab_diff_data)

@@

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_per") %>%
  select(eez_name,early,mid) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(avrg_spp_per = mean(early,na.rm=T))

>>>>

plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank()
  ) +
  guides(fill=guide_legend(title= "Level")) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 12,
  height = 7,
  units = "in"
  )

@@

Value_map_data <- Eme_value_data %>% 
  left_join(Total_value,
            by = c("fishing_entity_id","variable")) %>% 
  mutate(participation = (sum_value/tot_value)*100+2000)

@@

# Index_data <- Eez_d_hist %>% 
#   left_join(Value_map_data) %>% 
#   filter(
#     tresh == "Tresh_one",
#     metric == "mean_yr"
#   ) %>% 
#   group_by(sau_fishing_entity,fishing_entity_id,variable) %>% 
#   summarise(
#     toe = mean(value,na.rm=T),
#     # sum_value = sum(sum_value),
#     mean_part = mean(participation,na.rm=T)
#   ) %>% 
#   filter(!is.na(variable)) %>% 
#   # spread(variable,sum_value) %>% 
#   spread(variable,mean_part) %>% 
#   mutate(
#     imp = catch+value,
#     index = imp/toe
#   )

@@

# Get min and maximums
# min_index <- min(Index_data$index)
# max_index <- max(Index_data$index)

# Index_data <- Index_data %>% 
#   mutate(
    # index_norm =(index-min_index)/(max_index-min_index),
  #   index_2000 = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  # )

@@

# Value_map_data <- Index_data %>%
  # select(sau_fishing_entity,fishing_entity_id,
         # tresh,
         # variable,
         # participation = index_2000)

@@

for(i in 1:2){

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = Brazil_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = Brazil_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Participation (%)",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

kruskalmc(emerging_yr~un_sub_region, data = Reg_diff_data) %>% 
  as.data.frame() %>% 
  rownames_to_column("comparrison") %>% 
  # head()
  write_csv("kw_regional.csv")

@@

kruskalmc(emerging_yr~DemersPelag, data = Hab_diff_data) %>% 
  as.data.frame() %>% 
  rownames_to_column("comparrison") %>% 
  # head()
  write_csv("kw_habitat.csv")

@@

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(avrg_spp_per = mean(early,na.rm=T))
